\thetitle

### 2022-06-10 paper/paper.tex
"possible valuations possible"

\ifen 
We will represent approximate portfolio valuations using a fixed-point decimal with a precision of $P$, where $P$ is the number of digits to retain after the decimal point. Let $r[x] =  10^{-P}\lfloor 10^P x \rfloor$ denote the value of $x$ rounded down to its nearest fixed-point representation. Since $\bar U = \sum_{j\in \mathcal{C}} f_j t_j$ is an upper bound on the valuation of any portfolio, and since we will ensure that each fixed-point approximation is an underestimate of the portfolio's true valuation, the set $\mathcal{V}$ of possible valuations possible in the fixed-point framework is finite:
\else
포트폴리오의 근사적 가치를 정확도 $P$로 구성된 고정소수점 십진수(fixed-point decimal)로 나타내자. 다, $P$는 소수점 뒤에 등장하는 숫자의 수이다. 이때 $x$를 가장 가까운 고정소수점 십진수로 내림한 것을 $r[x] =  10^{-P}\lfloor 10^P x \rfloor$라고 하자. 임의의 포트폴리오의 가치가 $\bar U = \sum_{j\in \mathcal{C}} f_j t_j$를 넘을 수 없으며, 모든 포트폴리오 가치의 고정소수점 십진수 근사가 실제값보다 작게 나타내도록 한다. 따라서 고정소수점 환경에서 발생할 수 있는 포트폴리오 가치로 이루어진 집합 $\mathcal{V}$는 유한 집합이다.
\fi
\begin{equation}
\mathcal{V} = \Bigl\{0, 1\times 10^{-P}, 2\times 10^{-P}, \dots, r\bigl[\bar U- 1\times 10^{-P}\bigr], r\bigl[\bar U\bigr]\Bigr\}
\end{equation}
\ifen Then $|\mathcal{V} | = \bar U \times 10^P + 1$.
\else 그러면 $|\mathcal{V} | = \bar U \times 10^P + 1$이다.\fi

>>>>

\ifen 
We will represent approximate portfolio valuations using a fixed-point decimal with a precision of $P$, where $P$ is the number of digits to retain after the decimal point. Let $r[x] =  10^{-P}\lfloor 10^P x \rfloor$ denote the value of $x$ rounded down to its nearest fixed-point representation. Since $\bar U = \sum_{j\in \mathcal{C}} f_j t_j$ is an upper bound on the valuation of any portfolio, and since we will ensure that each fixed-point approximation is an underestimate of the portfolio's true valuation, the set $\mathcal{V}$ of  valuations observable in the fixed-point framework is finite:
\else
포트폴리오의 근사적 가치를 정확도 $P$로 구성된 고정소수점 십진수(fixed-point decimal)로 나타내자. 다, $P$는 소수점 뒤에 등장하는 숫자의 수이다. 이때 $x$를 가장 가까운 고정소수점 십진수로 내림한 것을 $r[x] =  10^{-P}\lfloor 10^P x \rfloor$라고 하자. 임의의 포트폴리오의 가치가 $\bar U = \sum_{j\in \mathcal{C}} f_j t_j$를 넘을 수 없으며, 모든 포트폴리오 가치의 고정소수점 십진수 근사가 실제값보다 작게 나타내도록 한다. 따라서 고정소수점 환경에서 발생할 수 있는 포트폴리오 가치로 이루어진 집합 $\mathcal{V}$는 유한 집합이다.
\fi
\begin{equation}
\mathcal{V} = \Bigl\{0, 1\times 10^{-P}, 2\times 10^{-P}, \dots, r\bigl[\bar U- 1\times 10^{-P}\bigr], r\bigl[\bar U\bigr]\Bigr\}
\end{equation}
\ifen Then $|\mathcal{V} | = \bar U \times 10^P + 1$.
\else 그러면 $|\mathcal{V} | = \bar U \times 10^P + 1$이다.\fi
